### 2024-04-13 thesis/chapters/06-conclusion.tex
Refactor jupyter

The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables. Annotations can be assigned belatedly or even never. Incremental learning kNN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label. The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.

>>>>

The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables. Annotations can be assigned belatedly or even never. Incremental learning k-NN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label. The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.

### 2024-04-13 thesis/chapters/analysis/1-condition-monitoring.tex
Refactor jupyter

Equipment's ``health'' can be mischaracterized when there are significant differences in the machine's normal operating conditions. Baseline measurements in all acceptable conditions are to be acquired to reduce the error in vibration evaluation. According to the bathtub curve~(Fig.~\ref{fig:bathtub-curve}) reference signatures should be obtained after the initial part wear-in period. The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band ~\cite{ziaran_technicka_2013}.

>>>>

Equipment's ``health'' can be mischaracterized when there are significant differences in the machine's normal operating conditions. Baseline measurements in all acceptable conditions are to be acquired to reduce the error in vibration evaluation. According to the bathtub curve~(Fig.~\ref{fig:bathtub-curve}) reference signatures should be obtained after the initial part wear-in period. The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band~\cite{ziaran_technicka_2013}.

### 2024-04-13 thesis/chapters/analysis/2-features.tex
Refactor jupyter

The other significant time domain attributes are derived as ratios of previous simpler ones. These ratios are crest, clearance, impulse factor, and shape factor~(Tab.~\ref{tab:td-features})~\cite{nandi_condition_2019}. Many articles have been successful in fault detection of bearings out of transients in impulsive signals with kurtosis, crest, and clearance factor \cite{brito_fault_2021}. It is also suggested that the shape factor can signify unbalance and misalignment faults~\cite{nandi_condition_2019}.

>>>>

The other significant time domain attributes are derived as ratios of previous simpler ones. These ratios are crest, clearance, impulse factor, and shape factor~(Tab.~\ref{tab:td-features})~\cite{nandi_condition_2019}. Many articles have been successful in fault detection of bearings out of transients in impulsive signals with kurtosis, crest, and clearance factor~\cite{brito_fault_2021}. It is also suggested that the shape factor can signify unbalance and misalignment faults~\cite{nandi_condition_2019}.

### 2024-04-13 thesis/chapters/analysis/3-diagnostics.tex
Refactor jupyter

\textbf{K-nearest neighbors} (KNN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:KNN}). It means it can work in a semi-supervised environment because it can infer labels just from knowing a few annotations. The major drawback of KNN is a preference for the majority class in imbalanced class-size datasets~\cite{shi_improving_2020}. The issue is mitigated with class weights or resampling classes by oversampling or undersampling. The KNN algorithm requires features to be normalized to assign the same importance to each predictor.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/analysis/KNN.png}
        \caption{KNN with k = 5}
        \label{fig:KNN}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/analysis/M-tree.png}
        \caption{M-tree data structure}
        \label{fig:m-tree}
    \end{subfigure}
    \caption{Nearest neighbors classification algorithm~\cite{chen_skyline_2009}}
\end{figure}

@@

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|}
\hline
\textbf{Distance}     & \textbf{$d(\mathbf{x}, \mathbf{y})$}                                   \\ \hline
Manhatann distance	 & $ |x_i - y_i| $													   \\ \hline
Euclidian distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
Mahalanobis distance  & $ (\mathbf{x} - \mathbf{y})^T C^{-1} (\mathbf{x} - \mathbf{y}) $       \\ \hline
\end{tabular}
\caption{Distance metrics for KNN}
\label{tab:KNN-distance}
\end{table}

The nearest-neighbor classifier has been successfully applied in machinery fault diagnostics. On the CWRU bearing dataset, the KNN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - KNN 91.2\%, SVM 88.8\%, and frequency domain features - KNN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.

Comparison of KNN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%. Best accuracy was reached for PSD features with 99.13\% with KLDA and 96.64\% with KNN classifiers and Mahalanobis metric. The sampling frequency was set at 40 kHz~\cite{altaf_new_2022}. Despite KNN lagging in accuracy, we have to keep in mind annotations for faults were complete, and machine learning was not tested in a streaming context.

>>>>

\textbf{K-nearest neighbors} (k-NN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:KNN}). It means it can work in a semi-supervised environment because it can infer labels just from knowing a few annotations. The major drawback of k-NN is a preference for the majority class in imbalanced class-size datasets~\cite{shi_improving_2020}. The issue is mitigated with class weights or resampling classes by oversampling or undersampling. The k-NN algorithm requires features to be normalized to assign the same importance to each predictor.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/analysis/KNN.png}
        \caption{k-NN with k = 5}
        \label{fig:KNN}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/analysis/M-tree.png}
        \caption{M-tree data structure}
        \label{fig:m-tree}
    \end{subfigure}
    \caption{Nearest neighbors classification algorithm~\cite{chen_skyline_2009}}
\end{figure}

@@

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{2}
\begin{tabular}{|l|l|}
\hline
\textbf{Distance}     & \textbf{$d(\mathbf{x}, \mathbf{y})$}                                   \\ \hline
Manhatann distance	 & $ |x_i - y_i| $													   \\ \hline
Euclidian distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
Mahalanobis distance  & $ (\mathbf{x} - \mathbf{y})^T C^{-1} (\mathbf{x} - \mathbf{y}) $       \\ \hline
\end{tabular}
\caption{Distance metrics for k-NN}
\label{tab:KNN-distance}
\end{table}

The nearest-neighbor classifier has been successfully applied in machinery fault diagnostics. On the CWRU bearing dataset, the k-NN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - k-NN 91.2\%, SVM 88.8\%, and frequency domain features - k-NN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.

Comparison of k-NN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%. Best accuracy was reached for PSD features with 99.13\% with KLDA and 96.64\% with k-NN classifiers and Mahalanobis metric. The sampling frequency was set at 40 kHz~\cite{altaf_new_2022}. Despite k-NN lagging in accuracy, we have to keep in mind annotations for faults were complete, and machine learning was not tested in a streaming context.

### 2024-04-13 thesis/chapters/analysis/4-datasets.tex
Refactor jupyter

\emph{MaFaulDa} dataset combines vibration and acoustic measurements of the shaft in deviating positions and bearings abnormalities. \emph{CWRU dataset} focuses solely on faults in ball bearings. Another less known dataset concerns shaft unbalance, but compared to the previous two, it demonstrates behavior during revolution speed up.

\subsection{Machinery Fault Database}
MaFaulDa\footnote{\url{https://www02.smt.ufrj.br/~offshore/mfs/page_01.html}} is a collection of 1951 multivariate time series for 4 different operational conditions on rotor kit Alignment Balance Vibration Trainer (ABVT)~(Fig.~\ref{fig:mafaulda-simulator}). Each series has 5~seconds in duration and is captured at 50 kHz. Vibration signals were obtained with piezoelectric accelerometers with a linear response up to 10~kHz, amplitude range to $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$.

@@

Observations were conducted in three cardinal axes simultaneously with 2 sets of accelerometers each one associated with one bearing (inner and outer bearings)~(Fig.~\ref{fig:mafaulda-simulator}). Additionally, a magnetic speedometer produced a pulse on shaft turn. The cardioid condenser microphone recorded sound emissions with a frequency range 20~Hz - 20~kHz. Sensors were fed into a four-channel dynamic signal acquisition module.

@@

This database contains normal operating conditions, faults out of unbalance, horizontal and vertical shaft misalignment, and three types of faulty bearings in inner and outer positions: outer track, inner track, rolling elements~\cite{pestana-viana_influence_2016}.
\begin{itemize}
\itemsep0pt
\item \textbf{Normal} conditions are baseline without the adverse effect of fault in 49 different rotation speeds. 
\item \textbf{Unbalance} shaft time series uses 8 unbalancing weights from 6 to 35 grams and varying 45 - 49 speeds for each weight adding to 333 mass unbalance loads. 
\item \textbf{Vertical misalignment} set is comprised of 50 signals each (or 51 in one instance) obtained under displacements: 0.51, 0.63, 1.40, 1.90, 1.27, 1.78 mm.
\item \textbf{Horizontal misalignment} signals were recorded under displacements: 0.50, 1.00, 1.50, 2.00 mm, each with 49 different speeds (or 50 in one instance)~\cite{pestana-viana_influence_2016}.
\item \textbf{Bearing faults} are unnoticeable without unbalance. Therefore, weights of 6, 20, and 35 grams were attached to induce a detectable effect. Each unbalance mass was combined with cage, outer race, and ball faults at multiple rotation speeds, usually at 50 different speeds.
\end{itemize}

@@

The sampling frequency during baseline set, drive end, and fan end bearing capture is 12 kHz, exclusively for drive end bearings samples were taken at 48 kHz. The duration of the time series is varied from 5 to 40 seconds. Drive end and fan end bearings signals are measured in each experiment. Accelerometer was sometimes mounted on the supporting base plate.

@@

The setup is shown in Fig.~\ref{fig:rotating-shaft}. Mass of 3.28 grams (or 6.61 grams during severe unbalance test) is attached to unbalance holder successively in 5 sets (numbered 0 - 4) on the radii 0, 14, 18.5, 23, 23 mm. The rotation speed of the motor is perpetually rising between 630 and 2330 rpm in development datasets (marked with suffix D) and speeds from 1060 to 1900 rpm in the evaluation datasets (suffix E). The vibrations were recorded at a sampling rate of 4 kHz~\cite{mey_machine_2020}.

@@

The accelerometers used are piezoelectric and have a frequency range of up to 10 kHz, dynamic range of $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$. These sensor parameters are the same as in the case of MaFaulDa. In total, three different uniaxial accelerometers are mounted on the motor housing.

>>>>

\emph{MaFaulDa} dataset combines vibration and acoustic measurements of the shaft in deviating positions and bearing abnormalities. \emph{CWRU dataset} focuses solely on faults in ball bearings. Another less known dataset concerns shaft unbalance, but compared to the previous two, it demonstrates behavior during speed up.

\subsection{Machinery Fault Database}
MaFaulDa\footnote{\url{https://www02.smt.ufrj.br/~offshore/mfs/page_01.html}} is a collection of 1951 multivariate time series for 4 different operational conditions on rotor kit Alignment Balance Vibration Trainer (ABVT)~(Fig.~\ref{fig:mafaulda-simulator}). Each series has 5~seconds in duration and is captured at 50 kHz. Vibration signals were obtained with piezoelectric accelerometers with a linear response up to 10~kHz, amplitude range to $\pm$490 $\mathrm{m/s}^2$, and resolution step of 10.2~mV per $\mathrm{m/s}^2$.

@@

Observations were conducted on three cardinal axes simultaneously with 2 sets of accelerometers, each one associated with one bearing (inner and outer bearings)~(Fig.~\ref{fig:mafaulda-simulator}). Additionally, a magnetic speedometer produced a pulse on shaft turn. The cardioid condenser microphone recorded sound emissions at a frequency range 20~Hz - 20~kHz. Sensors were fed into a four-channel dynamic signal acquisition module.

@@

This database contains normal operating conditions, faults out of unbalance, horizontal and vertical shaft misalignment, and three types of faulty bearings in inner and outer positions: outer track, inner track, rolling elements~\cite{pestana-viana_influence_2016}.

\begin{itemize}
\itemsep0pt

\item \textbf{Normal} conditions are baseline without the adverse effect of fault at 49 different rotation speeds.

\item \textbf{Unbalance} shaft time series uses 8 unbalancing weights from 6 to 35 grams and varying 45 - 49 speeds for each weight, adding to 333 mass unbalance loads.

\item \textbf{Vertical misalignment} set comprises 50 signals each (or 51 in one instance) obtained under displacements: 0.51, 0.63, 1.40, 1.90, 1.27, 1.78 mm.

\item \textbf{Horizontal misalignment} signals were recorded under displacements: 0.50, 1.00, 1.50, 2.00 mm, each with 49 different speeds (or 50 in one instance)~\cite{pestana-viana_influence_2016}.

\item \textbf{Bearing faults} are unnoticeable without unbalance. Therefore, weights of 6, 20, and 35 grams were attached to induce a detectable effect. Each mass was combined with cage, outer race, and ball faults at multiple rotation speeds, usually at 50 different speeds.
\end{itemize}

@@

The sampling frequency during baseline set, drive end, and fan end bearing capture is 12 kHz. For drive end bearings, samples were taken at 48 kHz. The duration of the time series varies from 5 to 40 seconds. Drive end and fan end bearing signals are measured in each experiment. Accelerometer was sometimes mounted on the supporting baseplate.

@@

The setup is shown in Fig.~\ref{fig:rotating-shaft}. A mass of 3.28 grams (or 6.61 grams during the severe unbalance test) is attached to the unbalance holder in 5 sets (numbered 0 - 4) on the radii 0, 14, 18.5, 23, 23 mm. The rotation speed of the motor is perpetually rising between 630 and 2330 rpm in development datasets (marked with suffix D) and speeds from 1060 to 1900 rpm in the evaluation datasets (suffix E). The vibrations were recorded at a sampling rate of 4~kHz~\cite{mey_machine_2020}.

@@

The accelerometers used are piezoelectric and have a frequency range of up to 10 kHz, dynamic range of $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $\mathrm{m/s}^2$. These sensor parameters are the same as in the case of MaFaulDa. In total, three different uniaxial accelerometers are mounted on the motor housing.

### 2024-04-13 thesis/chapters/appendix/C-user-guide.tex
Refactor jupyter

\thispagestyle{empty}
\chapter{Technical documentation} \label{appendix:technical-docs}
\pagenumbering{arabic}
\renewcommand*{\thepage}{C-\arabic{page}}

\section{Data collection plan}

The vibration measurements will occur monthly for pumps and biweekly for compressors from February 2024 until May 2024.
\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{|l|l|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|}
\hline
\textbf{Machine}                                                                      & \textbf{Placement \textbackslash Month} & \multicolumn{2}{p{1.2cm}|}{\textbf{02/2024}} & \multicolumn{2}{p{1.2cm}|}{\textbf{03/2024}} & \multicolumn{2}{p{1.2cm}|}{\textbf{04/2024}} \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC \#3\end{tabular}}} & SFTA001AT000TN                          &         &        &       &        &     &        \\ \cline{2-8} 
                                                                                      & SFTA002AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
                                                                                      & Steel base (noise)                      &         &        &       &        &     &         \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC \#5\end{tabular}}} & SFTA001AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
                                                                                      & SFTA002AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
                                                                                      & Steel base (noise)                      &         &        &       &        &     &         \\ \hline
\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#1\end{tabular}}} & MTRA001AT090TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#7\end{tabular}}} & MTRA001AT090TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
\multirow{6}{*}{\textbf{Pump Sigma}}                                                  & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
\end{tabular}
\end{table}
Each measurement will involve 3 trials for each position. The sensor is mounted to the machine with adhesive on double-sided carpet tape (placement notation follows MIMOSA convention from ISO~13373-1). After every trial, the sensor will be detached and attached again.

The plan was consulted and approved by the machinery owners: VNET~a.s. and Bratislavská vodárenská spoločnosť,~a.s. Triaxial recording has a duration 60~s (at $f_s$ = 26.7 kHz) and a 16-bit resolution. The total space requirements for 108 recordings are 990 MiB.

>>>>

\thispagestyle{empty}
\chapter{User Guide} \label{appendix:user-guide}
\pagenumbering{arabic}
\renewcommand*{\thepage}{C-\arabic{page}}

### 2024-04-13 thesis/chapters/appendix/E-work-plan.tex
Refactor jupyter

\thispagestyle{empty}
\chapter{Work plan}
\pagenumbering{arabic}
\renewcommand*{\thepage}{B-\arabic{page}}

@@

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting to set goals, and experiments and discuss the status of collaborations with partners.
\\ \hline
\nth{2} week         &  Arrange collaboration with an alternative industry partner. Prepare a checklist for the technical inspection of machinery. Construct a device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in the data center. Feature extraction step to calculate features from MaFaulDa.
 \\ \hline
\nth{4} week         & Consultation about plan for machine to measure in the data center and better device for measurement.
 \\ \hline
\nth{5} week         &  In feature selection using various metrics to determine sets of best features in the MaFaulDa.
 \\ \hline
\nth{6} week         & Feature selection used in k-NN multiclass and binary classificator.
 \\ \hline
\nth{7} week         & Explore incremental learning k-NN algorithm with MaFaulDa dataset. Consultation and status report.
 \\ \hline
 \nth{8} week         & Shorten analysis chapter about wavelets. Look at clustering detection incremental learning in MaFaulDa.
 \\ \hline
 \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for k-NN validation. Consultation to discuss progress.
 \\ \hline
  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning. Fix the sampling rate issue in the provisional sensor unit.
 \\ \hline
  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump.
 \\ \hline
  \nth{12} - \nth{15} week         &  Write up design chapter: research questions, visualization export. Finish writing chapter on design and implementation.
 \\ \hline
\end{tabular}
\end{table}

@@

\section{Summer semester - DP3}
\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1}  - \nth{2} week         & 
\begin{enumerate}
\itemsep0pt
\item Incorporate suggestions from DP2 defense. 
\item Develop and test firmware for designed sensor unit.
\end{enumerate}
\\ \hline
\nth{2}  - \nth{10} week         & 
\begin{enumerate}
\itemsep0pt
\item Long-term manual regular gathering of vibration data from compressors and pumps. 
\item Find optimal number of features. 
\item Try to increase k-NN prediction metrics.
\item Put together incremental learning with feature selection. 
\item Explore incremental clustering in search of method that can help with labeling.
\end{enumerate}
\\ \hline
\nth{10} - \nth{12} week         & Conclude results from measurements in real environment.
 \\ \hline
\end{tabular}
\end{table}

>>>>

\thispagestyle{empty}
\chapter{Work plan}
\pagenumbering{arabic}
\renewcommand*{\thepage}{E-\arabic{page}}

@@

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting to set goals, experiments and discuss the status of collaborations with partners.
\\ \hline
\nth{2} week         &  Arrange collaboration with an alternative industry partner. Prepare a checklist for the technical inspection of machinery. Construct a device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in the data center. Feature extraction step to calculate features from MaFaulDa.
 \\ \hline
\nth{4} week         & Consultation about plan for machine to measure in the data center and better device for measurement.
 \\ \hline
\nth{5} week         &  In feature selection using various metrics to determine sets of best features in the MaFaulDa.
 \\ \hline
\nth{6} week         & Feature selection used in k-NN multiclass and binary classificator.
 \\ \hline
\nth{7} week         & Explore incremental learning k-NN algorithm with MaFaulDa dataset. Consultation and status report.
 \\ \hline
 \nth{8} week         & Shorten analysis chapter about wavelets. Look at clustering detection incremental learning in MaFaulDa.
 \\ \hline
 \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for k-NN validation. Consultation to discuss progress.
 \\ \hline
  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning.
 \\ \hline
  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump. Desihn the firmware for new datalogger.
 \\ \hline
  \nth{12} - \nth{15} week         &  Write up design chapter: research questions and visualization export. Finish writing chapter on design and implementation.
 \\ \hline
\end{tabular}
\end{table}

@@

\section{Summer semester - DP3}
\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week  & Build and debug hardware of vibration logger with the consultant. 
\\ \hline
\nth{2} week & Implement and test firmware on standing fan for logging signal to SD card.
\\ \hline
\nth{3} week & First compressor (\nth{20} February) and water pump (\nth{27} and \nth{28} February) vibration measurements and their fault and frequency analysis. 
 \\ \hline
\nth{4} week & Replace two time domain features and evaluate on MaFaulDa and own dataset. Repeated measurement of compressors (\nth{5} March).
 \\ \hline
\nth{5} week & Perform PCA analysis of whole feature sets. Consultation about methods for own dataset evaluation.
 \\ \hline
\nth{6} week  & Consultation with experts in SjF STU. Formulate research goals for scientific paper and create graphs of the model results. Experiment with k-value and number of features to reach better accuracy. Repeated measurement of compressors (\nth{19} March).
 \\ \hline
\nth{7} week & Repeated measurement of water pumps (\nth{26} and \nth{27} March). Request and download data about pumps from KSB Cloud.
 \\ \hline
 \nth{8} week & Write up complete paper and submit to IIT.SRC student conference after feedback from supervisor.
 \\ \hline
 \nth{9} week & Refactor jupyter notebooks nad apply different labeling strategy applied in paper to incremental learning.
 \\ \hline
  \nth{10} week & Write up implementation chapter of the thesis.
 \\ \hline
  \nth{11} week & 
 \\ \hline
  \nth{12} - \nth{15} week &  
 \\ \hline
\end{tabular}
\end{table}

The aim of final semestre was to gather own dataset from compressors and water pumps with custom data logger. The k-NN model was validated with diffrent hyperparameters.
